Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-09-08 Paper.tex
update

@@

\section{Implementation}

In this last section we will describe some main aspect of our implementation.

>>>>

\section{System features}

@@

Any mapper send to LPP information about computed data like its size. Using all informations collected from each on-line WP during previous phase, LPP perform a locality-aware data shuffle according to which our system avoids transferring large partitions, shuffling smaller ones and saving network bandwidth.

Since, according to our design, any WPG can receive a partition from any other, we need to wait until all mappers complete to certainly designate all the network locations of partitions. When map phase is fully done and all the network locations known, LPP starts to coordinates shuffle phase, ordering to some or all WGs to move part of their data to precisely location. These location are computed in order to shuffle smaller partition only.

When shuffle phase is fully complete, LPP starts to coordinate $n$ Arbitrary-Fault-Tolerant Reduce Tasks (AFT-RTs) assigning them to every WPGs which now have all necessary data to perform this kind of operation. When all AFT-RTs fully finish, LPP perform another checkpoint in order to restore from an eventual LLP's crash.

If too many arbitrary errors occur, making AFT-RTs completion impossible, it's enough to restart current phase.

\subsection{Retrieve and Collect phase}

When reducer phase is fully done, LPP start to retrieve all reduce outputs from WPs. To be more precise, for every available WPG in system LPP picks a single WP which, according to data received during last phase, has computed correct outputs.

Then all reduce outputs are finally concatenated in an single output file by LPP which store these data into Zookeeper Cluster. LPP informs the client which can retrieve his output from Zookeeper cluster.
